Price of Anarchy for Mean Field Games

### 2018-07-21 PoA.tex
update prop 4 b_2 infty

% proposition b_2
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}

	%Moreover, if
	%	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + %\bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	%then
	%$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	%otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

	% b_2 to infty

	Now we consider the case when $b_2 \to \infty$. It can be seen later in the proof that both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$. In order to study the limit of $PoA$,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.

@@

>>>>

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

\begin{remark}
	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$. The idea here becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$. Indeed, we will show that $\Delta SC$ decreases exponentially fast when $b_2$ tends towards infinity while $SC^{MKV}$ decreases as fast as $1/b_2$. Therefore, the Price of Anarchy $PoA$ will decrease exponentially fast as $b_2 \to \infty$, which can also be observed in the numerical result hereafter. 
\end{remark}

\begin{proof}

@@

%proposition b_2 \to 0
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
\end{proposition}
